Supplement to ``Local clustering of density upper level sets''

### 2019-01-18 icml/icml_local_density_clustering_supplement.tex
began restructuring proof of theorem 2

\newcommand{\diam}{\mathrm{diam}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\1}{\mathbf{1}}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\Err}{\mathrm{Err}}

@@

@@

As part of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}, we will require an estimate of a function $g(t)$ for $t \in [x_0, 1/2]$ for some $x_0 > 0$. For $m > 0$ and $x_0 = t_0 < t_1 < \ldots < t_m = 1/2$, define the \emph{stepwise approximation to $g$} to be $\bar{g}$, given by 
\begin{equation}
\label{eqn: stepwise_approximation}
\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
\end{equation}
\begin{lemma}
	\label{lem: stepwise_approximation}
	Fix
	\begin{equation*}
	g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [x_0, 1/2]$}
	\end{equation*}
	 If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq x_0/2$, then $g(t) \geq \bar{g}(t)\geq g(t) / 2$.
\end{lemma}
\begin{proof}
	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function.

@@

@@

The $r$-ball walk over $\Csig$ is a Markov chain with transition probability for $x \in \Csig, \Sset, \Sset' \subset \Csig$ given by,
\begin{equation*}
P_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}, ~~~ Q_{\Pbb, r}(\Sset, \Sset') := \int_{x \in \Sset} f(x) P_{\Pbb, r}(x;\Sset') dx. 
\end{equation*}
stationary distribution defined by
\begin{equation*}
\ell_{\Pbb,r}(x) := \frac{\nu_\Pbb(\Csig \cap B(x,r))}{\nu_{\Pbb}(B(x,r))}, ~~~ \pi_{\Pbb,r}(\Sset) := \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \ell_{\Pbb,r}(x) dx
\end{equation*}
and corresponding conductance function
\begin{equation*}
\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}
\end{equation*}
Lemma \ref{lem: continuous_conductance_lb} (\textcolor{red}{a weighted analogue of Theorem 4.6 of Kannan}) provides a lower bound on $\widetilde{\Phi}_{\Pbb, r}(t)$, as well as a stepwise approximation to $\widetilde{\Phi}_{\Pbb, r}$.
\begin{lemma}
	\label{lem: continuous_conductance_lb}
	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following bounds hold: 
	\begin{itemize}
		\item 
		for $0 < t < 1/2$,
		\begin{equation*}
		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(\frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
		\end{equation*}
		\item
		Let
		\begin{equation*}
		m = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
		\end{equation*}
		 and $t_i = (i + 1)/m$ for $i = 0, \ldots, m - 1$. Then, for $1/m < t < 1/2$
		\begin{equation*}
		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\log\left(\frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
		\end{equation*}
		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{m - 1}$. 
	\end{itemize}

\end{lemma}
\begin{proof}
	We begin by stating directly the result of \textcolor{red}{Kannan et al.}: for $0 < t < 1/2$, and any $S$ such that $\pi_{\nu,r}(S) = t$,
	\begin{equation}
	\label{eqn: kannan_1}
	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{t} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(\frac{1}{t}\right)\right\}.
	\end{equation}
	Now, we note that
	\begin{equation*}
	\pi_{\Pbb,r}(S) \leq \pi_{\nu,r}(S) \cdot \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}, ~~~ Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset) \geq Q_{\nu,r}(\Sset, \Csig \setminus \Sset) \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
	\end{equation*}
	and plugging these estimates in to \eqref{eqn: kannan_1} gives the final bound on $\widetilde{\Phi}_{\Pbb,r}(t)$.  The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows immediately from application of Lemma \ref{lem: stepwise_approximation}.
\end{proof}

@@

\begin{lemma}
	\label{lem: consistency_of_conductance_function}
	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, fix any $0 < t < 1/2$. Then the following statement holds: with probability one, as $n \to \infty$,
	\begin{equation*}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t)
	\end{equation*}
	As a consequence, for $m$ and $(t_i)_{i=1}^{m}$ defined as in Lemma \ref{lem: continuous_conductance_lb}, we have that
	\begin{equation}
	\label{eqn: consistency_of_stepapprox_conductance_function}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
	\end{equation}
\end{lemma}
Lemma \ref{lem: consistency_of_conductance_function} stems from \textcolor{red}{Garcia Trillos 16}, with a pair of notable distinctions: here, we do not allow the radius $r$ to go to zero, but rather set it to be constant, and in the minimization we have an additional constraint on the measure $\pi(\cdot)$, in both the discrete and continuous functionals. As such, we will need to re-prove a number of the statements of \textcolor{red}{Garcia Trillos 16} to work in this context. We defer this work to Section \ref{subsection: proof_of_pointwise consitency_of_conductance_function}, and here will only show that  \eqref{eqn: consistency_of_stepapprox_conductance_function} is implied immediately by the pointwise result.

\begin{proof}[Proof of \eqref{eqn: consistency_of_stepapprox_conductance_function}]
We take as given that for any $0 < t < 1/2$,
\begin{equation*}
\lim_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
\end{equation*}
In particular, this will occur for $t_0, t_1, \ldots, t_m$ and therefore
\begin{equation*}
\lim_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
\end{equation*}
uniformly over $[1/m,1/2]$. But by Lemma \ref{lem: stepwise_approximation}, $\widetilde{\Phi}_{n,r} \geq \overline{\Phi}_{n,r}$, so we have shown \eqref{eqn: consistency_of_stepapprox_conductance_function}.
\end{proof}

@@

	To go between the two, we have
	\begin{align*}
	\norm{\deltabf^{(2t)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(t)}}^2_{L^{2}(\pi)} \\
	& = \norm{(\deltabf^{(t)})^2}^2_{L^{1}(\pi)} \\
	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(t)})}_{L^{1}(\pi)} \norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)}
	\end{align*}
	where $(i)$ is a result of \textcolor{red}{Benjamini and Morris} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
	\begin{align*}
	\norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{k  = 1,\ldots,N} \frac{(e_v\Wbf^t)[k]}{\pibf[k]} \right\} \\
	& \overset{(iii)}{\leq} \max\left\{1, \frac{\vol(V; G)}{d_{\min}(G)^2} \right\} \\
	& = \max\left\{1, \frac{1}{10 \pi_1(G)}\right\}
	\end{align*}
	where $(iii)$ follows from $\pibf[k] \geq d_{\min}(G) / \vol(V; G)$ and $(e_v\Wbf^t) \geq 1/d_{\min}$.

@@

>>>>

\newcommand{\diam}{\mathrm{diam}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\defeq}{\overset{\mathrm{def}}{=}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\1}{\mathbf{1}}
\newcommand{\var}{\mathrm{Var}}
\newcommand{\Err}{\mathrm{Err}}
\newcommand{\Log}{\mathrm{Log}}

@@

%%% Random walk vectors

@@

As part of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}, we will require an estimate of a function $g(t)$ for $t \in [x_0, 1/2]$ for some $x_0 > 0$. For $m > 0$ and $x_0 = t_0 < t_1 < \ldots < t_m = 1/2$, define the \emph{stepwise approximation to $g$} to be $\bar{g}$, given by 
\begin{equation}
\label{eqn: stepwise_approximation}
\bar{g}(t) = g(t_i), ~~ \text{ for $t \in [t_{i-1}, t_i]$ }
\end{equation}
\begin{lemma}
	\label{lem: stepwise_approximation}
	\begin{itemize}
		\item For any function $f$ monotone decreasing in $t$ on the interval $[x_0,1/2]$, $\bar{f}(t) \leq f(t)$ for all $t \in [x_0,1/2]$.
		\item Fix
		\begin{equation*}
		g(t) = \log\left(\frac{1}{t}\right) \text{ for $x \in [x_0, 1/2]$}
		\end{equation*}
		If for all $i$ in $1,\ldots,m$, $(t_i - t_{i - 1}) \leq x_0/2$, then $\bar{g}(t)\geq g(t) / 2$.
	\end{itemize}

\end{lemma}
\begin{proof}
	The first statement is immediately obvious, and we turn to proving the second.

	The upper bound $g(t) \geq \bar{g}(t)$ follows immediately from the fact that $g(t)$ is a decreasing function along with the first statement.

@@

\subsection{Mixing time on graphs}
For $N \in \mathbb{N}$ and a set $V$ of $N$ vertices, take $G = (V,E)$ to be an undirected and unweighted graph, with associated adjacency matrix $\Abf$, random walk matrix $\Wbf$, and stationary distribution $\pibf = (\pi_u)_{u \in V}$ where $\pi_v = \frac{\Dbf_{vv}}{\vol(V; G)}$. For $v \in V$, 
\begin{equation}
\label{eqn: random_walk}
q_{vu}^{(m)} = e_v\Wbf^m e_u, ~~ \qbf_{v}^{(m)} = \left(q_{vu}^{(m)}\right)_{u \in V}, ~~ \qbf_v = (\qbf^{(1)}_{v\cdot},\qbf^{(2)}_{v\cdot}, \ldots), 
\end{equation}
denote respectively the $m$-step transition probability, distribution, and sequence distributions of the random walk over $G$ originating at $v$. Letting $\qbf = (\qbf_v)_{v \in V}$, the relative pointwise mixing time is thus
\begin{equation*}
\tau_{\infty}(\qbf; G) = \min\set{m: \forall u,v \in V, \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \leq 1/4} 
\end{equation*}

Two key quantities relate the mixing time to the expansion of subsets $S$ of $V$. The \emph{local spread} is defined to be
\begin{equation*}
s(G) := \frac{9D_{\min}}{10}\pi_{\min} 
\end{equation*}
for $D_{\min} := \min_{v \in V} \Dbf_{vv}$ and $\pi_{\min} := D_{\min} / \vol(V; G)$.

%\inf \set{t: \forall S \subset V ~\text{with}~ \pi(S) = t, \beta(S) \leq 1/10}
%\end{equation*}
where $\beta(S) := \inf_{v \in S} \qbf_{v}^{(1)}(S^c)$, and by convention we let $\pbf(S) = \sum_{u \in S} p_u$ for any distribution vector $\pbf = (p_u)_{u \in V}$ over $V$. We collect some necessary facts about the local spread in Lemma \ref{lem: local_spread_G}.
\begin{lemma}
	\label{lem: local_spread_G}
	\begin{itemize}
		\item If $\pibf(S) \leq s(G)$, then for every $u \in S$, $\qbf_u^{(1)}(S) \geq 1/10$.
		\item For any $v, u \in V$, and $m \in N$ greater than $0$, $q_{vu}^{(m)}/ \pi_{\min} \leq 1/s(G)$.
	\end{itemize}

\end{lemma}

\begin{proof}
	If $t = \pibf(S) \leq \frac{9 D_{\min}}{10} \pi_{\min}$, divide both sides by $\pi_{\min}$ to obtain
	\begin{equation*}
	\abs{S} \leq \frac{9 D_{\min}}{10}
	\end{equation*}
	which implies $\qbf_{v}^{(1)}(S^c) \geq 1/10$ for all $v \in S$. This implies the first statement.

	The second statement follows from the fact $q_{vu}^{(m)} \leq 1/D_{\min}$ for any $m$.
\end{proof}

The local spread facilitates conversion between $\tau_{\infty}(\qbf_v; G)$ and the more easily manageable \emph{total variation} mixing time, given by
\begin{equation*}
\tau_1(\rhobf; G) = \min\biggl\{m: \forall v \in V, \norm{\rhobf_v - \pibf}_{TV} \leq 1/4 \biggr\}
\end{equation*}
where 
\begin{equation}
\label{eqn: uniform_random_walk}
\rhobf_{v}^{(m)} = \frac{1}{m}\sum_{k = 1}^{m+1} \qbf_{v}^{m}, ~~ \rhobf_v = \left( \rhobf_{v}^{(1)}, \rhobf_{v}^{(2)}, \rhobf_{v}^{(3)} \ldots \right), ~~ \rhobf = \left( \rhobf_v \right)_{v \in V}
\end{equation}
and $\norm{\pbf - \pibf}_{TV} = \sum_{v \in V}\abs{p_v - \pi_v}$ is the total variation norm between distributions $\pbf$ and $\pibf$. 
\begin{lemma}
	\label{lem: tv_mixing_to_pointwise_mixing1}
	For $\qbf$ as in \eqref{eqn: random_walk} and $\rhobf$ as in \eqref{eqn: uniform_random_walk},
	\begin{equation*}
	\tau_{\infty}(\qbf; G) \leq 2752 \tau_1(\rhobf; G) \log \left(4 \max\left\{1, \frac{1}{10 s(G)}\right\}\right)
	\end{equation*}
\end{lemma}
\begin{proof}
	Masking dependence on $v$ for the moment, let
	\begin{equation*}
	\Delta_u^{(m)} = q_{vu}^{(m)} - \pi_u, ~~ \delta_u^{(m)} = \frac{\Delta_u^{(m)}}{\pi_u}
	\end{equation*}
	and $\Deltabf^{(m)} = (\Delta_u^{(m)})_{u \in V}$, $\deltabf^{(m)} = (\delta_u^{(m)})_{u \in V}$. For a vector $\Deltabf = (\Delta_u)_{u \in V}$, the $L^{p}(\pibf)$ norm is given by
	\begin{equation*}
	\norm{\Deltabf}_{L^p(\pibf)} = \left(\sum_{u \in V} \left(\Delta_u\right)^{p} \pi_u \right)^{1/p}
	\end{equation*}
	To go between the $L^{\infty}(\pibf)$ and $L^{1}(\pibf)$ norms, we have
	\begin{align*}
	\norm{\deltabf^{(2m)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(m)}}^2_{L^{2}(\pi)} \\
	& = \norm{(\deltabf^{(m)})^2}_{L^{1}(\pi)} \\
	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(m)})}_{L^{1}(\pi)} \norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)}
	\end{align*}
	where $(i)$ is a result of \textcolor{red}{Benjamini and Morris} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
	\begin{align*}
	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{u \in V} \frac{q_{vu}^{(m)}}{\pi_u} \right\} \\
	& \overset{(iii)}{\leq} \max\left\{1, \frac{1}{s(G)}\right\}
	\end{align*}
	where $(iii)$ follows from Lemma \ref{lem: local_spread_G}.

	Now, we leverage the following well-known fact (\textcolor{red}{PhD thesis of Montenegro}): for any $\epsilon > 0$, if $m \geq \tau_1(\qbf_v^{(m)}; G) \cdot \log(1/\epsilon)$ then
	\begin{equation*}
	\norm{\qbf_v^{(m)} - \pibf}_{TV} \leq \epsilon.
	\end{equation*}
	But $\norm{\qbf_v^{(m)} - \pibf}_{TV}$ is exactly $\norm{(\deltabf^{(m)})}_{L^{1}(\pi)}$. Therefore, picking 
	\begin{equation*}
	m_0 = \tau_1(\qbf_v^{(m)}; G) \cdot \log \left(4 \max\left\{1, \frac{1}{s(G)}\right\} \right)
	\end{equation*} implies $\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} \leq 1/4$ for all $m \geq 2 m_0$.  Then, 
	\begin{equation*}
	\norm{(\deltabf^{(m)})}_{L^{\infty}(\pi)} = \sup_{u}\left\{ \frac{\abs{q_{vu}^{(m)} - \pibf_u}}{\pibf_u} \right\}.
	\end{equation*}
	and since none of the above depended on a specific choice for $v$, the supremum can be taken over all seed nodes $v$ as well. Thus $\tau_{\infty}(\qbf^{(m)}; G) \leq 2m_0$.

	Finally, it is known (\textcolor{red}{PhD thesis of Montenegro}) that
	\begin{equation*}
	\tau_{1}(\qbf^{(m)}; G) \leq 1376 \tau_{1}(\rhobf^{(m)}; G)
	\end{equation*}
	and so the desired result holds.

The second key quantity is the \emph{conductance function}
\begin{equation*}
\Phi(t; G) := \min_{\substack{S \subseteq V, \\ \pibf(S) \leq t} } \Phi(S; G) ~~~~~~~ (\pi_{\min} \leq t < 1)
\end{equation*}
where $\Phi(S; G)$ is the normalized cut of $S$ in $G$ given by \eqref{eqn: norm_cut}.

@@

The $r$-ball walk over $\Csig$ is a Markov chain with transition probability for $x \in \Csig, \Sset, \Sset' \subset \Csig$ given by,
\begin{equation*}
P_{\Pbb, r}(x;\Sset) := \frac{\nu_\Pbb(\Sset \cap B(x,r))}{\nu_\Pbb(\Csig \cap B(x,r))}, ~~~ Q_{\Pbb, r}(\Sset, \Sset') := \int_{x \in \Sset} f(x) P_{\Pbb, r}(x;\Sset') dx. 
\end{equation*}
stationary distribution defined by
\begin{equation*}
\ell_{\Pbb,r}(x) := \frac{\nu_\Pbb(\Csig \cap B(x,r))}{\nu_{\Pbb}(B(x,r))}, ~~~ \pi_{\Pbb,r}(\Sset) := \frac{1}{\int_{\Csig} f(x) \ell_{\Pbb,r}(x) dx} \int_{\Sset} f(x) \ell_{\Pbb,r}(x) dx
\end{equation*}
and corresponding conductance function
\begin{equation*}
\widetilde{\Phi}_{\Pbb,r}(t) := \min_{\substack{\Sset \subset \Csig, \\ \pi_{\Pbb,r}(\Sset) \leq t} } \frac{Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset)}{\pi_{\Pbb,r}(\Sset)}
\end{equation*}
Lemma \ref{lem: continuous_conductance_lb} (\textcolor{red}{a weighted analogue of Theorem 4.6 of Kannan}) provides a lower bound on $\widetilde{\Phi}_{\Pbb, r}(t)$, as well as a stepwise approximation to $\widetilde{\Phi}_{\Pbb, r}$.
\begin{lemma}
	\label{lem: continuous_conductance_lb}
	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following bounds hold: 
	\begin{itemize}
		\item 
		for $0 < t < 1/2$,
		\begin{equation*}
		\widetilde{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
		\end{equation*}
		\item
		Let
		\begin{equation*}
		m = \frac{2^{d+1}D^d \Lambda_{\sigma}^2}{r^d \lambda_{\sigma}^2}
		\end{equation*}
		 and $t_i = (i + 1)/m$ for $i = 0, \ldots, m - 1$. Then, for $1/m < t < 1/2$
		\begin{equation*}
		\overline{\Phi}_{\Pbb,r}(t) > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{162 \sqrt{d}D}\Log\left( \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2 t}\right)\right\} \cdot \frac{\lambda_{\sigma}^4}{\Lambda_{\sigma}^4}
		\end{equation*}
		where $\overline{\Phi}_{\Pbb,r}(t)$ is defined as in \eqref{eqn: stepwise_approximation} with respect to $t_0, \ldots t_{m - 1}$, and $\Log(A/t) = \max\{\log(1 + 2A), \log(A/t)\}$.
	\end{itemize}

\end{lemma}
\begin{proof}
	We begin by stating directly the result of \textcolor{red}{Kannan et al.}: for $0 < t < 1/2$, and any $S$ such that $\pi_{\nu,r}(S) = t$,
	\begin{equation}
	\label{eqn: kannan_1}
	\frac{Q_{\nu,r}(\Sset, \Csig \setminus \Sset)}{t} > \min\left\{\frac{1}{288\sqrt{d}},\frac{r}{81 \sqrt{d}D}\log\left(1 + \frac{1}{t}\right)\right\}.
	\end{equation}
	Now, we note that
	\begin{equation*}
	\pi_{\Pbb,r}(S) \leq \pi_{\nu,r}(S) \cdot \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}, ~~~ Q_{\Pbb,r}(\Sset, \Csig \setminus \Sset) \geq Q_{\nu,r}(\Sset, \Csig \setminus \Sset) \cdot \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2}
	\end{equation*}

	and plugging these estimates in to \eqref{eqn: kannan_1} gives the final bound on $\widetilde{\Phi}_{\Pbb,r}(t)$.  The bound on $\overline{\Phi}_{\Pbb,r}(t)$ then follows from  $\Log(A/t) \leq \log(1 + 1/t)$ for all $0 < t < 1/2$ and application of Lemma \ref{lem: stepwise_approximation}.
\end{proof}

@@

\begin{lemma}
	\label{lem: consistency_of_conductance_function}
	Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, fix any $0 < t < 1/2$. Then the following statement holds: with probability one, as $n \to \infty$,
	\begin{equation*}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t)
	\end{equation*}
	As a consequence, for $m$ and $(t_i)_{i=1}^{m}$ defined as in Lemma \ref{lem: continuous_conductance_lb}, we have that
	\begin{equation}
	\label{eqn: consistency_of_stepapprox_conductance_function}
	\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
	\end{equation}
\end{lemma}
Lemma \ref{lem: consistency_of_conductance_function} stems from \textcolor{red}{Garcia Trillos 16}, with a pair of notable distinctions: here, we do not allow the radius $r$ to go to zero, but rather set it to be constant, and in the minimization we have an additional constraint on the measure $\pi(\cdot)$, in both the discrete and continuous functionals. As such, we will need to re-prove a number of the statements of \textcolor{red}{Garcia Trillos 16} to work in this context. We defer this work to Section \ref{subsection: proof_of_pointwise consitency_of_conductance_function}, and here will only show that  \eqref{eqn: consistency_of_stepapprox_conductance_function} is implied immediately by the pointwise result.

\begin{proof}[Proof of \eqref{eqn: consistency_of_stepapprox_conductance_function}]
We take as given that for any $0 < t < 1/2$,
\begin{equation*}
\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \widetilde{\Phi}_{\Pbb,r}(t).
\end{equation*}
In particular, this will occur for $t_0, t_1, \ldots, t_m$ and therefore
\begin{equation*}
\liminf_{n \to \infty} \overline{\Phi}_{n,r} \geq \overline{\Phi}_{\Pbb,r}
\end{equation*}
uniformly over $[1/m,1/2]$.
\end{proof}

@@

	To go between the two, we have
	\begin{align*}
	\norm{\deltabf^{(2t)}}_{L^{\infty}(\pi)} & \overset{(i)}{\leq} \norm{\deltabf^{(t)}}^2_{L^{2}(\pi)} \\
	& = \norm{(\deltabf^{(t)})^2}_{L^{1}(\pi)} \\
	& \overset{(ii)}{\leq}  \norm{(\deltabf^{(t)})}_{L^{1}(\pi)} \norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)}
	\end{align*}
	where $(i)$ is a result of \textcolor{red}{Benjamini and Morris} and $(ii)$ follows from Holder's inequality. Now, we upper bound the second factor on the right hand side by observing
	\begin{align*}
	\norm{(\deltabf^{(t)})}_{L^{\infty}(\pi)} & \leq \max\left\{1, \max_{k  = 1,\ldots,N} \frac{(e_v\Wbf^t)[k]}{\pibf[k]} \right\} \\
	& \overset{(iii)}{\leq} \max\left\{1, \frac{\vol(V; G)}{d_{\min}(G)^2} \right\} \\
	& = \max\left\{1, \frac{1}{10 \pi_1(G)}\right\}
	\end{align*}
	where $(iii)$ follows from $\pibf[k] \geq d_{\min}(G) / \vol(V; G)$ and $(e_v\Wbf^t) \geq 1/d_{\min}$.

@@

\begin{proof}[Proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}]
	Fix arbitrary $v = x_i \in \Csig[\Xbf]$, and let
	\begin{equation*}
	\widetilde{q}_n^{(t)} = e_v \Wbf_{\Csig[\Xbf]}^t, ~~ \widetilde{\qbf}_n = (\widetilde{q}_n^{(1)}, \widetilde{q}_n^{(2)}, \ldots)
	\end{equation*}
	be the distribution of a random walk over the subgraph $G_{n,r}[\Csig[\Xbf]]$ after $t$. For simplicity, we will refer to the subgraph $G_{n,r}[\Csig[\Xbf]]$ as $\widetilde{G}_{n,r}$ hereafter. Our goal is to upper bound $\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.

	By Lemma \ref{lem: tv_mixing_to_pointwise_mixing}, 
	\begin{equation*}
	\tau_{\infty}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq 2752 \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \max\left\{2, \log\left(\frac{4}{10 \widetilde{\pi}_{1,n}}\right) \right\}
	\end{equation*}

	We first upper bound $\tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r})$.  From Lemma \ref{lem: montenegro}, we have that
	\begin{equation*}
	\limsup_{n \to \infty} \tau_{1}(\widetilde{\qbf}_n; \widetilde{G}_{n,r}) \leq \limsup_{n \to \infty} \frac{1400}{3}\left(5 + \int_{x = \widetilde{\pi}_{1,n}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} dx\right)
	\end{equation*}
	We set aside the constant term for the moment and turn to the integral. By Lemma \ref{lem: local_spread_lb},
	\begin{equation*}
	\limsup_{n \to \infty}\int_{x = \widetilde{\pi}_{1,n}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} \leq \limsup_{n \to \infty}\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} dx
	\end{equation*}
	where $\pi_{1,\Pbb,r} = \frac{\lambda_{\sigma}^2}{\Lambda_{\sigma}^2} \frac{r^d}{(2D)^d}$. We now replace the discrete conductance function $\widetilde{\Phi}_{n,r}$ by the continuous conductance function $\overline{\Phi}_{n,r}$:
	\begin{align*}
	\limsup_{n \to \infty}\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\widetilde{\Phi}_{n,r}^2(x)} dx & \overset{(i)}{\leq} \limsup_{n \to \infty}\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\overline{\Phi}_{n,r}^2(x)} dx \\
	& = \int_{x = \pi_{1,\Pbb,r}}^{1/2} \limsup_{n \to \infty} \frac{4}{\overline{\Phi}_{n,r}^2(x)} dx \\
	& \overset{(ii)}{\leq} \int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\overline{\Phi}_{\Pbb,r}^2(x)} dx \\
	\end{align*}
	where $(i)$ follows from Lemma \ref{lem: stepwise_approximation} and $(ii)$ from Lemma \ref{lem: consistency_of_conductance_function} (along with the continuous mapping theorem). Now, we make use of the lower bound on the continuous conductance function of Lemma \ref{lem: continuous_conductance_lb}:
	\begin{align*}
	& \int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{4}{\overline{\Phi}_{\Pbb,r}^2(x)} dx \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
	\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{d}{x} dx + \int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{81dD^2}{r^2x \Log(\frac{\Lambda_{\sigma}^2}{x\lambda_{\sigma}^2})}  \right) dx \\
	& \leq \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} \cdot \left( 331776
	\underbrace{\int_{x = \pi_{1,\Pbb,r}}^{1/2} \frac{d}{x} dx}_{:= \mathcal{J}_1} + 
	81\underbrace{\int_{x = \pi_{1,\Pbb,r}}^{\lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)} \frac{dD^2}{r^2x \log(\frac{\Lambda_{\sigma}^2}{x\lambda_{\sigma}^2})}}_{:= \mathcal{J}_2} +
	81\underbrace{\int_{x = \lambda_{\sigma}^2/(4 \Lambda_{\sigma}^2)}^{1/2} \frac{dD^2}{r^2x \log(1 + \frac{4 \lambda_{\sigma}^2}{\Lambda_{\sigma}^2})}}_{:= \mathcal{J}_3}  \right)
	\end{align*}
\end{proof}

Simple integration yields the following upper bounds on $\mathcal{J}_1, \mathcal{J}_2, \mathcal{J}_3$:
\begin{align*}
\mathcal{J}_1 & \leq d^2 \log\left( \frac{2D\Lambda_{\sigma}^2}{r\lambda_{\sigma}^2} \right) \\
\mathcal{J}_2 & \leq \frac{dD^2}{r^2} \left[ \log\left(2d\right) + \log\left(\log\left(\frac{2d}{r}\right)\right) \right] \\
\mathcal{J}_3 & \overset{(iii)}{\leq} 2 \frac{dD^2}{r^2} \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2} \log\left(4 \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2}\right)
\end{align*}
where $(iii)$ uses the upper bound $\frac{1}{\log(1 + x)} \leq \frac{1}{x}$.
